FHJ: A Formal Model for Hierarchical Dispatching and Overriding

### 2018-01-13 ECOOP18/sections/RelatedWork.tex
submitted

\begin{figure}[t]
	\saveSpaceFig
	\begin{lstlisting}
mixin HelloWorld of Object =
	new Object MainMatter()
	begin
		"Hello world".String.print();
	end;
end;
(new HelloWorld []).HelloWorld.MainMatter();
	\end{lstlisting}
	\caption{Full-qualified name of method calls in Magda.}
	\label{fig:magda_prefix}
	\saveSpaceFig
\end{figure}

\begin{figure*}[t]
	\saveSpaceFig
\begin{lstlisting}
mixin A of Object =
	new String m()
	begin
		return "A";
	end;
end;

mixin B of Object = 
	new String m()
	begin
		return "B";
	end;
end;

mixin C of A, B = 
	new String m()
	begin
		return "C";
	end;
end;
\end{lstlisting}
	\caption{Code in Magda.}
	\label{fig:magda_code}
	\saveSpaceFig
\end{figure*}

>>>>

\begin{figure*}[t]
	\saveSpaceFig
	\begin{lstlisting}
mixin HelloWorld of Object =
	new Object MainMatter()
	begin
		"Hello world".String.print();
	end;
end;
(new HelloWorld []).HelloWorld.MainMatter();
	\end{lstlisting}
	\caption{Full-qualified name of method calls in Magda.}
	\label{fig:magda_prefix}
	\saveSpaceFig
\end{figure*}

\begin{figure*}[t]
	\saveSpaceFig
\begin{lstlisting}
mixin A of Object =
	new String m()
	begin
		return "A";
	end;
end; 
mixin B of Object = 
	new String m()
	begin
		return "B";
	end;
end;
mixin C of A, B = 
	new String m()
	begin
		return "C";
	end;
end;
\end{lstlisting}
	\caption{Code in Magda.}
	\label{fig:magda_code}
	\saveSpaceFig
\end{figure*}
